Optimal (Multiway) Spatial Joins

### 2024-06-02 msj.tex
yufei

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type2:contained-h*}.}

\noindent \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\cross_{R_{k-2}}(\bm{t}) = \cross_{R_{k-2}}(h^*)$. We can then derive that
\myeqn{
    \sum_{h^* \in H^*} |\cross_{R_{k-2}}(h^*)| \le \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\cross_{R_{k-2}}(\bm{t})| \leq \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

Now, we explain the mapping. Consider an arbitrary $h^* \in H^*$. Recall that $h^*$ is the minimal segment of some segment $h' \in H'$. Specifically, if $h' = [x_1,x_2]\times y$, then $h^* = [x_1,\minleft(h')]\times y$. By the definition of $\minleft(h')$ in \eqref{eqn:hv:type2:H*}, there exists a tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$ satisfying $\bm{t}[k-2] = h'$ and $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$}$. We map $h^*$ to $\bm{t}$.

@@

Next, we will prove that a rectangle $r_{k-2} \in \cross_{R_{k-2}}(h^*)$ if and only if $r_{k-2} \in \cross_{R_{k-2}}(\bm{t})$. By the definition of $\cross_{R_{k-2}}(h^*)$ and $\cross_{R_{k-2}}(\bm{t})$ (see Definition~\eqref{eqn:contained} and \eqref{eqn:type2:contained-t}), it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$. Let $x$ be the $x$-coordinate of the vertical segment $\bm{t}[k-1]$. Then, $B_\bm{t}$, which is the intersection of $h'$ and $v$, is $(x,y)$, where $y$ is the $y$-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$.

>>>>

\extraspacing {\bf Proof of Lemma~\ref{lmm:hv:type2:contained-h*}.} We will prove each statement in turn.

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\cross_{R_{k-2}}(\bm{t}) = \cross_{R_{k-2}}(h^*)$. We can then derive that
\myeqn{
    \sum_{h^* \in H^*} |\cross_{R_{k-2}}(h^*)| \le \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\cross_{R_{k-2}}(\bm{t})| \leq \out, \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

Now, we explain the mapping. Consider an arbitrary $h^* \in H^*$. Recall that $h^*$ is the minimal segment of some segment $h' \in H'$. Specifically, if $h' = [x_1,x_2]\times y$, then $h^* = [x_1,\minleft(h')]\times y$. By the definition of $\minleft(h')$ in \eqref{eqn:hv:type2:H*}, there exists a tuple $\bm{t}\in \J(R_1',...,R_{k-2}')$ satisfying $\bm{t}[k-2] = h'$ and $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$}$ (recall that $\bm{t}[k-1]$ is a vertical segment). We map $h^*$ to $\bm{t}$.

@@

Next, we will prove that a rectangle $r_{k-2} \in \cross_{R_{k-2}}(h^*)$ if and only if $r_{k-2} \in \cross_{R_{k-2}}(\bm{t})$. By the definition of $\cross_{R_{k-2}}(h^*)$ and $\cross_{R_{k-2}}(\bm{t})$ --- defined in  \eqref{eqn:contained} and \eqref{eqn:type2:contained-t}, respectively --- it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$. Let $x$ be the $x$-coordinate of the vertical segment $\bm{t}[k-1]$. Then, $B_\bm{t}$, which is the intersection of $h'$ and $v$, is $(x,y)$, where $y$ is the $y$-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$.
